Twists of supersymmetric gauge theories

### 2019-08-13 paper.tex
Continuing edits to SYM section

\brian{recall dfn of $\oloc$ of a gr vb.}

@@

\begin{dfn}
Let $(E, Q,\omega, I)$ be a classical field theory 
A {\bf strict action} of a super Lie algebra $\fg$ on $(E, Q,\omega, I)$ is a map of super dg Lie algebras (in differentiable pro-cochain complexes)
\[
\rho\colon \fg \to \left(\oloc(E)[-1] , \{-,-\}_\omega, Q + \{I,-\}_\omega\right) .
\]
More generally, an $L_\infty$ {\bf action} is an $\infty$-morphism of super dg Lie algebras
\[
\rho\colon \fg \rightsquigarrow \left(\oloc(E)[-1] , \{-,-\}_\omega, Q + \{I,-\}_\omega\right) .
\]
\brian{maybe point to appendix where we can fix conventions for $\infty$-maps}
\end{dfn}

We denote components of an $\infty$-morphism by $\rho_2, \rho_3, \dots$, so that $\rho_2$ is a morphism of (super) chain complexes.

@@

@@

In this section, we will consider pairs $(\mf A, \fL)$ consisting of a supersymmetry algebra and an instance of Yang-Mills theory with matter, in one of the following four situations.
\begin{itemize}
 \item Dimension $n=3$ with $\Sigma = S$, the 2-dimensional Dirac representation.
 \item Dimension $n=4$ with $\Sigma = S_+ \oplus S_-$, 4-dimensional Dirac representation.
 \item Dimension $n=6$ with $\Sigma = S_+ \otimes W$ where $W$ is a 2-dimensional symplectic vector space, the 8-dimensional symplectic Weyl representation.
 \item Dimension $n=10$ with $\Sigma = S_+$, the 16-dimensional Weyl representation.
\end{itemize}
We'll construct, in each of these cases, an $L_\infty$ action of the super Lie algebra $\mf A$ on the theory $\fL$.  This construction will proceed in two steps.
\begin{enumerate}
 \item There is an ordinary Lie action of the super Lie algebra $\mf A$ on the theory $\fL$, extending the standard action of the $n$-dimensional Poincar\'e algebra by isometries of $\RR^{n}$ \chris{define this above}, which is only well-defined on-shell.  In other words, there is a linear map $\delta^{(1)} \colon \mf A \to \cloc^\bu(\fL)[-1]$ which is a Lie action modulo the ideal generated by the equations of motion \chris{induces a Lie homomorphism on cohomology?}.
 \item We can promote this on-shell action to an $L_\infty$ map $\delta^{(1)} \colon \mf A \to \cloc^\bu(\fL)[-1]$ by including a quadratic term $\delta^{(2)}$ which ``corrects'' for the failure of the map $\delta^{(1)}$ to be a Lie map on-the-nose.
\end{enumerate}
This construction only works in the four special dimensions $3,4,6$ and 10: our argument will use results of Baez and Huerta \cite{BaezHuerta} proven using the structure of the four normed division algebras $\RR, \CC, \bb H$ and $\bb O$.  In particular, we will use the following ``3-$\psi$'s rule'' \chris{see citations in Baez Huerta for more references, which we might include}.  Let $g(v,w)$ denote the Riemannian metric on $\RR^n$.
%We will write $\wt \Sigma$ for the spin representation obtained from $\Sigma$ by parity reversal, so in dimensions 3 and 4 $\wt \Sigma = \Sigma$, in dimension 6 $\wt \Sigma = S_- \otimes W$, and in dimension 10 $\wt \Sigma = S_-$.

\begin{theorem}[{\cite[Theorem 11]{BaezHuerta}}]
The multilinear map 
\[T \colon \Sigma \otimes \Sigma \otimes \Sigma \otimes \Sigma \to \CC,\]
obtained by symmetrizing the expression $g(\Gamma(\psi_1,\psi_2), \Gamma(\psi_3, \psi_4))$ in the first three variables, is zero.
\end{theorem}

@@

So, we start by discussing the on-shell supersymmetry.  The fermionic part of the supersymmetry algebra is defined by saying that $Q \in \Sigma$ acts infinitesimally by
\[
\begin{pmatrix}
A \\ \lambda
\end{pmatrix}
\mapsto
\begin{pmatrix} A + \delta_Q A \\
\lambda + \delta_Q \lambda
\end{pmatrix}
\]
where 
\begin{align*}
\delta_Q A &= \Gamma(Q,\lambda) \\
\delta_Q \lambda &= \sd F_A Q .
\end{align*}
Here, the notation $\sd F_A$ stands for the iterated Clifford multiplication $\sd F_A = F_{ij} \gamma^i \gamma^j$.  We can check that this supersymmetry action does not close off-shell.  Indeed \chris{...}

\chris{heavily edit the below.}
\begin{lemma} \label{10d_onshell_lemma}
Suppose $Q_1, Q_2 \in S_+$ and $(A, \lambda)$ are fields.
The following relations hold:
\begin{itemize}
\item[(1)] \label{10dsusyA} $ [\delta_{Q_1}, \delta_{Q_2}] A = \delta_{[Q_1, Q_2]} A$.
\item[(2)] \label{10dsusyL} $ [\delta_{Q_1}, \delta_{Q_2}] \lambda = \delta_{[Q_1,Q_2]} \lambda - \rho(\Gamma(Q_1,Q_2)) \sd \dd \lambda - \frac 12(Q_2, \sd \dd \lambda)Q_1 - \frac 12(Q_2, \sd \dd \lambda)Q_2$ .
\end{itemize}
Here, the commutator on the left hand side of the equations takes place in the algebra of endomorphisms of the space of fields.
\end{lemma}

\begin{proof}
Both are direct calculations using standard Clifford relations which cite below.
So, we calculate
\begin{align*}
[\delta_{Q_1}, \delta_{Q_2}] A &= (\Gamma(Q_2,\sd F_A Q_1) + \Gamma(Q_1,\sd F_A Q_2)) \\
&=  F_{ij}(Q_2 \gamma^k \gamma^j \gamma^i Q_1 + Q_1 \gamma^k \gamma^j \gamma^i Q_2) \\
&=  F_{ij}(Q_2 \gamma^k \gamma^j \gamma^i Q_1 + Q_2 \gamma^i \gamma^j \gamma^k Q_1)\\
&= F_{ij}(\delta^{jk}(Q_2\gamma^i Q_i) - Q_2 \gamma^i \gamma^j \gamma^k + Q_2 \gamma^i \gamma^j \gamma^k Q_1)\\
&=  F_{ij}\delta^{jk}(Q_2 \gamma^i Q_1) \\
&= \delta_{[Q_1, Q_2]} A,
\end{align*}
where on the third line we used the fact that the pairing $\Gamma(-,-)$ is symmetric -- i.e. that $\lambda_1 \gamma^i \lambda_2 = \lambda_2 \gamma^i \lambda_1$ -- and on the fourth line we used the Clifford relation $\gamma^j\gamma^j+\gamma^j\gamma^j = \delta^{jk}$.  Note that, on the gauge fields, the action is a Lie action on the nose, not only on-shell.  Similarly we can calculate, following the calculation in Guillen \cite{Guillen}:
\begin{align*}
[\delta_{Q_1}, \delta_{Q_2}] \lambda &= (\sd F_{\Gamma(Q_2, \lambda)} Q_1 + \sd F_{\Gamma(Q_1,\lambda)} Q_2) \\
&= \frac 12((Q_2 (\gamma_j \dd_i - \gamma_i \dd_j) \lambda) (\gamma^i \gamma^j Q_1) + (1 \leftrightarrow 2)) \\
&= \frac 12((Q_2 \gamma_j \dd_i \lambda) \gamma^i \gamma^j Q_1 + (Q_1 \gamma_j \dd_i \lambda) \gamma^i \gamma^j Q_2) - \frac 12((Q_2 \gamma_i \dd_j \lambda) \gamma^i \gamma^j Q_1 + (Q_1 \gamma_i \dd_j \lambda) \gamma^i \gamma^j Q_2) \\
&= \frac 12((Q_2 \gamma_j \dd_i \lambda) \gamma^i \gamma^j Q_1 + (Q_1 \gamma_j \dd_i \lambda) \gamma^i \gamma^j Q_2) + \frac 12((Q_2 \gamma_i \dd_j \lambda) \gamma^j \gamma^j Q_1 + (Q_1 \gamma_i \dd_j \lambda) \gamma^j \gamma^i Q_2) + \\
&\quad - \frac 12((Q_2 \gamma_i \dd_j \lambda) \delta_{ij} Q_1 + \frac 12(Q_1 \gamma_i \dd_j \lambda) \delta^{ij} Q_2) \\
&= ((Q_1 \gamma_j Q_2) (\gamma^i \gamma^j \dd_i \lambda) - \frac 12(Q_2 \gamma_i \dd_i \lambda)Q_1 - \frac 12(Q_1 \gamma_i \dd_i \lambda)Q_2
\end{align*}
using the fact that 
\[(\psi_1 \gamma_j \psi_2)(\gamma^j \psi_3) + (\psi_2 \gamma_j \psi_3)(\gamma^j \psi_1) + (\psi_3 \gamma_j \psi_1)(\gamma^j \psi_2) = 0,\]
as in \cite[Theorem 11]{BaezHuerta}.  Making one more simplification using the Clifford relations, we have
\begin{align*}
[\delta_{Q_1}, \delta_{Q_2}] \lambda &= ((Q_1 \gamma_j Q_2) (\delta^{ij} \dd_i \lambda) - ((Q_1 \gamma_j Q_2) (\gamma^j \gamma^i \dd_i \lambda) - \frac 12(Q_2 \gamma_i \dd_i \lambda)Q_1 - \frac 12(Q_1 \gamma_i \dd_i \lambda)Q_2 \\
&= \delta_{[Q_1,Q_2]} \lambda - \rho(\Gamma(Q_1,Q_2)) \sd \dd \lambda - \frac 12(Q_2, \sd \dd \lambda)Q_1 - \frac 12(Q_2, \sd \dd \lambda)Q_2.
\end{align*}
\end{proof}

In particular the supersymmetry action is a Lie algebra homomorphism only modulo the ideal generated by the equation of motion $\sd \dd \lambda = 0$.
In other words, this supersymmetry action only defined an action of the Lie algebra of supertranslations ``on-shell".  This calculation suggests introducing a second order correction to the supersymmetry action on the BV theory, which has the chance of closing off-shell.  Define a second order action depending on the antifield $\lambda^*$ to the gluino $\lambda$ by
\begin{align*}
\delta^{(2)} \colon S_+ \otimes S_+ \otimes \Gamma(\RR^{10}; \Pi S_-[-1]) &\to \Gamma(\RR^{10}; \Pi S_+) \\
Q_1 \otimes Q_2 \otimes \lambda^* &\mapsto - \left(\rho(\Gamma(Q_1,Q_2)) \lambda^* + \frac 12 \left((Q_2, \lambda^*)Q_1 + (Q_1, \lambda^*)Q_2\right)\right).
\end{align*}

We'll rewrite this as a local functional in the theory $\fL$ coupled to the $\mc N=(1,0)$ super Lie algebra $\mf A$.

@@

\begin{prop}
Let $S_{\mr{BV}}$ be the BV action functional in the theory $\fL$, and write $I_{\mr{Poin}}$ for the interaction generating the Lie action of the Poincar\'e algebra. The functional
\[\fS = S_{\mr{BV}} + I_{\mr{Poin}} + I^{(1)} + I^{(2)} \in \clie^\bu(\mc A) \otimes \cloc^\bu(\fL) [-1]\]
satisfies the Maurer-Cartan equation
\begin{equation} 
\label{10d_MC}
(\d_{\rm Lie} \fS + \frac{1}{2} \left\{\fS , \fS \right\} = 0 .
\end{equation}
\end{prop}

\chris{we'll have to see whether we want Poincar\'e or just translation here, probably translation, because then there are no $\d_{\mr{Lie}}I^{(i)}$ terms to worry about.  On the other hand we would like to know that the theories are supersymmetric, not just super-translation invariant.  To include rotations and R-symmetries we need to additionally check that some terms like $\d_{\mr{Lie}}+ \{I_{\mr{rotation}} + I_{\text{R-symmetry}}, I^{(i)}\}$ vanish.}

\begin{proof}
We can filter the complex $\clie^\bu(\mc A) \otimes \cloc^\bu(\fL)$ by the number of anti-field components in $\fL$.  Using this filtration, the left-hand side of \ref{10d_MC} splits up as
\begin{align}
\d_{\rm Lie}  \left( \fS \right) + \frac{1}{2} \left\{ \fS , \fS \right\} &= \d_{\mr{Lie}} I_{\mr{Poin}} + \frac 12 \{S_{\mr{BV}} + I_{\mr{Poin}}, S_{\mr{BV}} + I_{\mr{Poin}}\} \label{10d_MC_BV}\\
&\quad + \{S_{\mr{BV}}, I^{(1)}\} \label{10d_MC_1}\\
&\quad + \d_{\mr{Lie}} I^{(1)} + \{S_{\mr{BV}}, I^{(2)}\} + \{I_{\mr{Poin}}, I^{(1)}\} + \frac 12 \{I^{(1)}, I^{(1)}\} \label{10d_MC_2}\\
&\quad + \d_{\mr{Lie}} I^{(2)} + \{I_{\mr{Poin}}, I^{(2)}\} + \{I^{(1)}, I^{(2)}\} \label{10d_MC_3}\\
&\quad + \frac 12 \{I^{(2)}, I^{(2)}\}. \label{10d_MC_4}
\end{align}
Taking these terms one at a time, we first note that the vanishing of \ref{10d_MC_BV} is just the fact that the BV action of the 10d super Yang-Mills theory satisfies the classical master equation, along with the fact that this theory is Poincar\'e invariant \chris{ref some earlier discussion}.  The remaining terms are those involving the action of supersymmetries.

First, the term \ref{10d_MC_1} vanishes by \chris{We've discussed this.  First the $\{I_{\mr{Poin}}, I^{(i)}\}$ terms vanish by Poincar\'e invariance of the interaction terms.  Then \ref{10d_MC_1} is zero by Baez--Huerta.  Term \ref{10d_MC_2} is Lemma \ref{10d_onshell_lemma}. Term \ref{10d_MC_3} vanishes because, first $\d_{\mr{Lie}}I^{(2)} = 0$ since ...not sure right now..., then the remaining term vanishes by the trick where we symmetrize in three spinors.  Finally \ref{10d_MC_4} vanishes because $I^{(2)}$ only involves antifields.}

\chris{apart from the Lemma \ref{10d_onshell_lemma}, this is all completely identical for dimensions 3,4,6,10.  Even that lemma only uses abstract gamma matrix manipulations that work in any dimension along with the Baez Huerta rule that applies in those dimensions, so I think we should just state a single result valid for those four theories simultaneously.}
\end{proof}

>>>>

\brian{recall dfn of $\oloc$ of a gr vb.} \chris{before the definition below we should probably define the antibracket $\{,\}$ (in terms of the shifted symplectic structure).}

@@

\begin{dfn} \label{infinitesimal_action_def}
Let $(E, Q,\omega, I)$ be a classical field theory 
A {\bf strict action} of a super Lie algebra $\fg$ on $(E, Q,\omega, I)$ is a map of super dg Lie algebras (in differentiable pro-cochain complexes)
\[
\rho\colon \fg \to \left(\oloc(E)[-1] , \{-,-\}_\omega, Q + \{I,-\}_\omega\right) .
\]
More generally, an $L_\infty$ {\bf action} is an $\infty$-morphism of super dg Lie algebras
\[
\rho\colon \fg \rightsquigarrow \left(\oloc(E)[-1] , \{-,-\}_\omega, Q + \{I,-\}_\omega\right) .
\]
\brian{maybe point to appendix where we can fix conventions for $\infty$-maps} \chris{Can we also give the definition here of an equivariant classical field theory in terms of the Maurer-Cartan / equivariant classical master equation?}
\end{dfn}

We denote components of an $\infty$-morphism by $\rho_2, \rho_3, \dots$, so that $\rho_2$ is a morphism of (super) chain complexes. \chris{below we define it in terms of an interaction with components $I^{(1)}, I^{(2)}$ etc, so we should give that point of view here as well.}

@@

We'll conclude this section with a discussion of the Poincar\'e invariance of classical Yang-Mills theory.

\begin{definition}
The $n$-dimensional \emph{Poincar\'e group} is the group $\mr{ISO}(n) = \SO(n) \ltimes \RR^n$ of isometries of $\RR^n$ with its flat Riemannian metric.  The $n$-dimensional \emph{Poincar\'e algebra} $\mf{iso}(n)$ is the Lie algebra of the Poincar\'e group.
\end{definition}

The $n$-dimensional Poincar\'e algebra acts, in the sense of definition \ref{infinitesimal_action_def}, on Yang-Mills theory on $\RR^n$ for any choice $\Sigma$ of matter representation.
\chris{define the interaction functional $I_\mr{Poin}$ associated to the Poincar\'e action on Yang-Mills theory.}

\begin{prop} \label{YM_Poincare_invariant_prop}
Yang-Mills theory is \emph{Poincar\'e invariant}.  That is, the classical BV action functional satisfies the Maurer-Cartan equation
\[\d_{\mr{Lie}}I_{\mr{Poin}} + \frac 12 \{S_{\mr{BV}} + I_{\mr{Poin}}, S_{\mr{BV}} + I_{\mr{Poin}}\}.\]
\end{prop}

\begin{proof}
\chris{...}
\end{proof}

@@

In this section, we will consider pairs $(\mf A, \fL)$ consisting of a supersymmetry algebra and an instance of Yang-Mills theory with matter, in one of the following four situations.
\begin{itemize}
 \item Dimension $n=3$ with $\Sigma = S$, the 2-dimensional Dirac representation.
 \item Dimension $n=4$ with $\Sigma = S_+ \oplus S_-$, 4-dimensional Dirac representation.
 \item Dimension $n=6$ with $\Sigma = S_+ \otimes W$ where $W$ is a 2-dimensional symplectic vector space, the 8-dimensional symplectic Weyl representation.
 \item Dimension $n=10$ with $\Sigma = S_+$, the 16-dimensional Weyl representation.
\end{itemize}

\begin{definition}
In each case we will write $\wt \Sigma$ for the spin representation obtained from $\Sigma$ by parity reversal, so in dimensions 3 and 4 $\wt \Sigma = \Sigma$, in dimension 6 $\wt \Sigma = S_- \otimes W$, and in dimension 10 $\wt \Sigma = S_-$.
\end{definition}

We'll construct, in each of these cases, an $L_\infty$ action of the super Lie algebra $\mf A$ on the theory $\fL$.  This construction will proceed in two steps.
\begin{enumerate}
 \item There is an ordinary Lie action of the super Lie algebra $\mf A$ on the theory $\fL$, extending the standard action of the $n$-dimensional Poincar\'e algebra by isometries of $\RR^{n}$ \chris{define this above}, which is only well-defined on-shell.  In other words, there is a linear map $\delta^{(1)} \colon \mf A \to \cloc^\bu(\fL)[-1]$ which is a Lie action modulo the ideal generated by the equations of motion \chris{induces a Lie homomorphism on cohomology?}.
 \item We can promote this on-shell action to an $L_\infty$ map $\delta^{(1)} \colon \mf A \to \cloc^\bu(\fL)[-1]$ by including a quadratic term $\delta^{(2)}$ which ``corrects'' for the failure of the map $\delta^{(1)}$ to be a Lie map on-the-nose.
\end{enumerate}
This construction only works in the four special dimensions $3,4,6$ and 10: our argument will use results of Baez and Huerta \cite{BaezHuerta} proven using the structure of the four normed division algebras $\RR, \CC, \bb H$ and $\bb O$.  In particular, we will use the following ``3-$\psi$'s rule'' \chris{see citations in Baez Huerta for more references, which we might include}.  Let $g(v,w)$ denote the Riemannian metric on $\RR^n$.

\begin{theorem}[{\cite[Theorem 11]{BaezHuerta}}] \label{3_psi_thm}
The multilinear map 
\[T \colon \Sigma \otimes \Sigma \otimes \Sigma \otimes \Sigma \to \CC,\]
obtained by symmetrizing the expression $g(\Gamma(\psi_1,\psi_2), \Gamma(\psi_3, \psi_4))$ in the first three variables, is zero.
\end{theorem}

@@

So, we start by discussing the on-shell supersymmetry.  The fermionic part of the supersymmetry algebra is defined by saying that $Q \in \Sigma$ acts infinitesimally by
\[
\begin{pmatrix}
A \\ \lambda
\end{pmatrix}
\mapsto
\begin{pmatrix} A + \delta_Q A \\
\lambda + \delta_Q \lambda
\end{pmatrix}
\]
where 
\begin{align*}
\delta_Q A &= \Gamma(Q,\lambda) \\
\delta_Q \lambda &= \sd F_A Q .
\end{align*}
Here, the notation $\sd F_A$ stands for the iterated Clifford multiplication $\sd F_A = F_{ij} \gamma^i \gamma^j$.  We can check that this supersymmetry action does not close off-shell.

\begin{lemma} \label{onshell_action_lemma}
Suppose $Q_1, Q_2 \in \Sigma$ and $(A, \lambda)$ are super Yang-Mills fields.
The following relations hold:
\begin{itemize}
\item[(1)] \label{10dsusyA} $ [\delta_{Q_1}, \delta_{Q_2}] A = \delta_{[Q_1, Q_2]} A$.
\item[(2)] \label{10dsusyL} $ [\delta_{Q_1}, \delta_{Q_2}] \lambda = \delta_{[Q_1,Q_2]} \lambda - \rho(\Gamma(Q_1,Q_2)) \sd \dd \lambda - \frac 12(Q_2, \sd \dd \lambda)Q_1 - \frac 12(Q_2, \sd \dd \lambda)Q_2$ .
\end{itemize}
Here, the commutator on the left hand side of the equations takes place in the algebra of endomorphisms of the space of fields.
\end{lemma}

\begin{proof}
\chris{todo:rewrite}
Both are direct calculations using standard Clifford relations which cite below.
So, we calculate
\begin{align*}
[\delta_{Q_1}, \delta_{Q_2}] A &= (\Gamma(Q_2,\sd F_A Q_1) + \Gamma(Q_1,\sd F_A Q_2)) \\
&=  F_{ij}(Q_2 \gamma^k \gamma^j \gamma^i Q_1 + Q_1 \gamma^k \gamma^j \gamma^i Q_2) \\
&=  F_{ij}(Q_2 \gamma^k \gamma^j \gamma^i Q_1 + Q_2 \gamma^i \gamma^j \gamma^k Q_1)\\
&= F_{ij}(\delta^{jk}(Q_2\gamma^i Q_i) - Q_2 \gamma^i \gamma^j \gamma^k + Q_2 \gamma^i \gamma^j \gamma^k Q_1)\\
&=  F_{ij}\delta^{jk}(Q_2 \gamma^i Q_1) \\
&= \delta_{[Q_1, Q_2]} A,
\end{align*}
where on the third line we used the fact that the pairing $\Gamma(-,-)$ is symmetric -- i.e. that $\lambda_1 \gamma^i \lambda_2 = \lambda_2 \gamma^i \lambda_1$ -- and on the fourth line we used the Clifford relation $\gamma^j\gamma^j+\gamma^j\gamma^j = \delta^{jk}$.  Note that, on the gauge fields, the action is a Lie action on the nose, not only on-shell.  Similarly we can calculate, following the calculation in Guillen \cite{Guillen}:
\begin{align*}
[\delta_{Q_1}, \delta_{Q_2}] \lambda &= (\sd F_{\Gamma(Q_2, \lambda)} Q_1 + \sd F_{\Gamma(Q_1,\lambda)} Q_2) \\
&= \frac 12((Q_2 (\gamma_j \dd_i - \gamma_i \dd_j) \lambda) (\gamma^i \gamma^j Q_1) + (1 \leftrightarrow 2)) \\
&= \frac 12((Q_2 \gamma_j \dd_i \lambda) \gamma^i \gamma^j Q_1 + (Q_1 \gamma_j \dd_i \lambda) \gamma^i \gamma^j Q_2) - \frac 12((Q_2 \gamma_i \dd_j \lambda) \gamma^i \gamma^j Q_1 + (Q_1 \gamma_i \dd_j \lambda) \gamma^i \gamma^j Q_2) \\
&= \frac 12((Q_2 \gamma_j \dd_i \lambda) \gamma^i \gamma^j Q_1 + (Q_1 \gamma_j \dd_i \lambda) \gamma^i \gamma^j Q_2) + \frac 12((Q_2 \gamma_i \dd_j \lambda) \gamma^j \gamma^j Q_1 + (Q_1 \gamma_i \dd_j \lambda) \gamma^j \gamma^i Q_2) + \\
&\quad - \frac 12((Q_2 \gamma_i \dd_j \lambda) \delta_{ij} Q_1 + \frac 12(Q_1 \gamma_i \dd_j \lambda) \delta^{ij} Q_2) \\
&= ((Q_1 \gamma_j Q_2) (\gamma^i \gamma^j \dd_i \lambda) - \frac 12(Q_2 \gamma_i \dd_i \lambda)Q_1 - \frac 12(Q_1 \gamma_i \dd_i \lambda)Q_2
\end{align*}
using the fact that 
\[(\psi_1 \gamma_j \psi_2)(\gamma^j \psi_3) + (\psi_2 \gamma_j \psi_3)(\gamma^j \psi_1) + (\psi_3 \gamma_j \psi_1)(\gamma^j \psi_2) = 0,\]
as in \cite[Theorem 11]{BaezHuerta}.  Making one more simplification using the Clifford relations, we have
\begin{align*}
[\delta_{Q_1}, \delta_{Q_2}] \lambda &= ((Q_1 \gamma_j Q_2) (\delta^{ij} \dd_i \lambda) - ((Q_1 \gamma_j Q_2) (\gamma^j \gamma^i \dd_i \lambda) - \frac 12(Q_2 \gamma_i \dd_i \lambda)Q_1 - \frac 12(Q_1 \gamma_i \dd_i \lambda)Q_2 \\
&= \delta_{[Q_1,Q_2]} \lambda - \rho(\Gamma(Q_1,Q_2)) \sd \dd \lambda - \frac 12(Q_2, \sd \dd \lambda)Q_1 - \frac 12(Q_2, \sd \dd \lambda)Q_2.
\end{align*}
\end{proof}

In particular the supersymmetry action is a Lie algebra homomorphism only modulo the ideal generated by the equation of motion $\sd \dd \lambda = 0$.
In other words, this supersymmetry action only defined an action of the Lie algebra of supertranslations ``on-shell".  This calculation suggests introducing a second order correction to the supersymmetry action on the BV theory, which has the chance of closing off-shell.  Define a second order action depending on the antifield $\lambda^*$ to the gluino $\lambda$ by
\begin{align*}
\delta^{(2)} \colon \Sigma \otimes \Sigma \otimes \Gamma(\RR^{n}; \Pi \wt \Sigma[-1]) &\to \Gamma(\RR^{n}; \Pi \Sigma) \\
Q_1 \otimes Q_2 \otimes \lambda^* &\mapsto - \left(\rho(\Gamma(Q_1,Q_2)) \lambda^* + \frac 12 \left((Q_2, \lambda^*)Q_1 + (Q_1, \lambda^*)Q_2\right)\right).
\end{align*}

We'll rewrite this as a local functional in the theory $\fL$ coupled to the supersymmetry Lie algebra $\mf A$.

@@

We can rephrase Lemma \ref{onshell_action_lemma} in terms of these local functionals.
\begin{lemma} \label{onshell_interaction_lemma}
The functionals $I^{(1)}$ and $I^{(2)}$ above satisfy the equation
\[\{I^{(1)},I^{(1)}\} = - 2\{S_{\mr{BV}} , I^{(2)}\}.\]
\end{lemma}

\begin{proof}
This is really just an alternative way of writing the statement of Lemma \ref{onshell_action_lemma}.  Indeed \chris{...}
\end{proof}

The functionals $I^{(1)}$ and $I^{(2)}$ are also rotation invariant, in the following sense.
\begin{lemma} \label{SUSY_rotation_invariance_lemma}
Let $I_{\mr{rot}}$ be the interaction associated to the action of $\so(n)$ on super Yang-Mills theory from Theorem \ref{YM_Poincare_invariant_prop}.  The functionals $I^{(1)}$ and $I^{(2)}$ are rotation invariant, meaning that
\[\d_{\mr{Lie}} I^{(i)} = - \{I_{\mr{rot}}, I^{(i)}\},\]
for $i=1,2$.
\end{lemma}

\begin{proof}
\chris{...}
\end{proof}

Now that we've defined the supersymmetry action, we can prove the main theorem of this section: that minimal super Yang-Mills theory in dimensions $n=3,4,6$ and 10 is, indeed, a supersymmetric classical field theory.

\begin{theorem} \label{SUSY_YM_theorem}
Let $S_{\mr{BV}}$ be the BV action functional in the theory $\fL$, and write $I_{\mr{Poin}}$ for the interaction generating the Lie action of the Poincar\'e algebra. The functional
\[\fS = S_{\mr{BV}} + I_{\mr{Poin}} + I^{(1)} + I^{(2)} \in \clie^\bu(\mf A) \otimes \cloc^\bu(\fL) [-1]\]
satisfies the Maurer-Cartan equation
\begin{equation} 
\label{nd_MC}
(\d_{\rm Lie} \fS + \frac{1}{2} \left\{\fS , \fS \right\}) = 0 .
\end{equation}
\end{theorem}

\begin{proof}
We can filter the complex $\clie^\bu(\mf A) \otimes \cloc^\bu(\fL)$ by the number of anti-field components in $\fL$.  Using this filtration, the left-hand side of \ref{nd_MC} splits up as
\begin{align}
\d_{\rm Lie}  \left( \fS \right) + \frac{1}{2} \left\{ \fS , \fS \right\} &= \d_{\mr{Lie}} I_{\mr{Poin}} + \frac 12 \{S_{\mr{BV}} + I_{\mr{Poin}}, S_{\mr{BV}} + I_{\mr{Poin}}\} \label{MC_BV}\\
&\quad + \{S_{\mr{BV}}, I^{(1)}\} \label{MC_1}\\
&\quad + \d_{\mr{Lie}} I^{(1)} + \{I_{\mr{Poin}}, I^{(1)}\} + \{S_{\mr{BV}}, I^{(2)}\} + \frac 12 \{I^{(1)}, I^{(1)}\} \label{MC_2}\\
&\quad + \d_{\mr{Lie}} I^{(2)} + \{I_{\mr{Poin}}, I^{(2)}\} + \{I^{(1)}, I^{(2)}\} \label{MC_3}\\
&\quad + \frac 12 \{I^{(2)}, I^{(2)}\}. \label{MC_4}
\end{align}
Taking these terms one at a time, we first note that the vanishing of the first term, \ref{MC_BV}, is just the fact that the BV action of the 10d super Yang-Mills theory satisfies the classical master equation, and is Poincar\'e invariant, as in Proposition \ref{YM_Poincare_invariant_prop}. The remaining terms are those involving the action of supersymmetries.

First, the term \ref{MC_1} vanishes by \cite[Proposition 14]{BaezHuerta}.  Baez and Huerta prove that in our four critical dimensions \chris{argue why this is the same}.

In the next term, \ref{MC_2}, the first two summands vanish by Lemma \ref{SUSY_rotation_invariance_lemma}, and the last two summands vanish by Lemma \ref{onshell_interaction_lemma}.  Likewise, in term \ref{MC_3}, the first two summands vanish by Lemma \ref{SUSY_rotation_invariance_lemma}, and the last term vanishes by applying the 3-$\psi$ rule, Theorem \ref{3_psi_thm}.  Indeed \chris{...}.

Finally, term \ref{MC_4} vanishes because the interaction $I^{(2)}$ only involves antifields: the BV antibracket of two expressions involving only antifields is always zero.
\end{proof}

\chris{Discuss dimensional reduction, and then the inclusion of the action of R-symmetries.}
